---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = TRUE,
  echo = TRUE,
  comment = "#>",
  fig.path = "README-",
  message=FALSE,
  warning=FALSE
)
```

# hiddenmeta ![R](https://github.com/gerasy1987/hiddenmeta/workflows/R/badge.svg) [![codecov](https://codecov.io/gh/gerasy1987/hiddenmeta/branch/main/graph/badge.svg?token=ZG9A64Q0A1)](https://codecov.io/gh/gerasy1987/hiddenmeta) [![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://github.com/gerasy1987/hiddenmeta/blob/main/LICENSE)

## Install and load packages

```{r install, eval=FALSE}

install.packages("DeclareDesign")
install.packages("igraph")

devtools::install_github("gerasy1987/hiddenmeta", build_vignettes = TRUE)

```

```{r setup}

library(hiddenmeta)
library(DeclareDesign)
library(igraph)

```

## Step 1. Provide study design features

```{r example_study_1}

## STUDY 1
study_1 <- 
  list(
    pop = 
      list(
        handler = get_study_population,
        network_handler = sim_block_network,
        network_handler_args = 
          list(N = 2000, K = 2, prev_K = c(known = .3, hidden = .1), rho_K = .05,
               p_edge_within = list(known = c(0.05, 0.05), hidden = c(0.05, 0.9)),
               p_edge_between = list(known = 0.05, hidden = 0.01),
               directed = FALSE),
        
        group_names = c("known", "hidden"),
        
        # probability of visibility (show-up) for each group
        p_visibility = list(known = .99, hidden = .7),
        
        # probability of service utilization in hidden population
        # for service multiplier
        add_groups = list(p_service = 0.3, 
                          loc_1 = 0.3, loc_2 = 0.1, loc_3 = 0.2, 
                          known_2 = 0.1, known_2 = 0.2)
      ),
    sample = 
      list(
        rds = list(handler = sample_rds,
                   # RDS parameters
                   sampling_variable = "rds",
                   n_seed = 20,
                   n_coupons = 3,
                   target_type = "sample",
                   target_n_rds = 100),
        tls = list(handler = sample_tls,
                   sampling_variable = "tls",
                   # TLS sampling parameters
                   target_n_tls = 1),
        pps = list(handler = sample_pps,
                   sampling_variable = "pps",
                   # prop sampling parameters
                   target_n_pps = 400)
      ),
    estimands = list(handler = get_study_estimands),
    estimators = 
      list(
        rds = 
          list(sspse = list(handler = get_study_est_sspse, 
                            label = "rds_sspse",
                            prior_median = 150,
                            rds_prefix = "rds"),
               chords = list(handler = get_study_est_chords,  
                             type = "integrated", 
                             label = "rds_chords")),
        pps = 
          list(ht = list(handler = get_study_est_ht, 
                         label = "pps_ht"),
               nsum = list(handler = get_study_est_nsum, 
                           label = "pps_nsum"))
      )
  )

```

## Step 2. Declare study population

```{r example_pop}

study_population <-
  do.call(what = declare_population,
          args = study_1$pop)

set.seed(19872312)
( example_pop <- study_population() )

```

### Show the network

```{r example_network, fig.width=6, fig.height=8}

g <-
  example_pop %$% {
    igraph::graph_from_adj_list(links,
                                mode = "all") %>%
      igraph::set_vertex_attr("name", value = name) %>%
      igraph::set_vertex_attr("type", value = type)
  }

igraph::V(g)$color <-
  plyr::mapvalues(igraph::V(g)$type,
                  from = unique(igraph::V(g)$type),
                  to = grDevices::palette.colors(n = length(unique(igraph::V(g)$type)), palette = "Set 3"))

plot(g,
     layout = igraph::layout_on_grid(g, dim = 2, width = 100),
     vertex.size = 3, vertex.dist = 2, vertex.label = NA, edge.width = 1,
     edge.arrow.size = .2, edge.curved = .2)

legend(x = -1, y = -1.2,
       legend = c("none", "known only", "hidden only", "both"),
       pt.bg = grDevices::palette.colors(n = length(unique(igraph::V(g)$type)), palette = "Set 3"),
       pch = 21, col = "#777777", pt.cex = 2, cex = 1.5, bty = "o", ncol = 2)

```

## Step 3. Declare all relevant study sampling procedures

The sampling procedures are additive in a sense that each procedure appends several columns relevant to the sampling procedure and particular draw based on population simulation, but does not change the study population data frame (unless you specify `drop_nonsampled = TRUE`).

```{r example_rds}
study_sample_rds <- 
  do.call(what = declare_sampling, 
          args = study_1$sample$rds)

set.seed(19872312)
draw_data(study_population + study_sample_rds)
```

```{r example_pps}
study_sample_pps <- 
  do.call(what = declare_sampling, 
          args = study_1$sample$pps)

set.seed(19872312)
draw_data(study_population + study_sample_rds + study_sample_pps)
```

```{r example_tls}
study_sample_tls <- 
  do.call(what = declare_sampling, 
          args = study_1$sample$tls)

set.seed(19872312)
draw_data(study_population + 
            study_sample_rds + study_sample_pps + study_sample_tls)
```

## Step 4. Declare study level estimands

```{r example_estimands}
study_estimands <- 
  do.call(what = declare_estimand, 
          args = study_1$estimands)

set.seed(19872312)
draw_estimands(study_population + 
                 study_sample_rds + study_sample_pps + study_sample_tls + 
                 study_estimands)
```

## Step 5. Declare estimators used in the study

```{r example_estimators}
estimator_sspse <- do.call(what = declare_estimator, 
                           args = study_1$estimators$rds$sspse)
estimator_chords <- do.call(what = declare_estimator, 
                            args = study_1$estimators$rds$chords)
estimator_ht <- do.call(what = declare_estimator, 
                        args = study_1$estimators$pps$ht)
estimator_nsum <- do.call(what = declare_estimator, 
                          args = study_1$estimators$pps$nsum)

set.seed(19872312)
draw_estimates(study_population +
                 study_sample_rds + study_sample_pps + study_sample_tls +
                 study_estimands +
                 estimator_sspse + estimator_ht + estimator_chords + estimator_nsum)
```

## Step 6. Diagnose study design

```{r example_diagnose, eval=FALSE}
study_diagnosands <-
 declare_diagnosands(
    mean_estimand = mean(estimand),
    mean_estimate = mean(estimate),
    sd_estimate = sd(estimate),
    mean_se = mean(se),
    bias = mean(estimate - estimand),
    rmse = sqrt(mean((estimate - estimand) ^ 2))
  )

diagnose_design(
  study_population + 
    study_sample_rds + study_sample_pps + 
    study_estimands + 
    estimator_sspse + estimator_ht + estimator_chords + estimator_nsum, 
  diagnosands = study_diagnosands,
  sims = 10,
  bootstrap_sims = 10)
```

## Meta-analysis Draft structure

1. Get all estimates produced for each of the studies (depending on the design) in a single data frame that will include estimator and standard error for each estimator (or potentially for each sampling-estimator pair) 
2. Then we can _feed_ this data frame into Stan model akin the one below
    a. Use the data frame to produce observed estimator vectors for each estimator/sampling-estimator pair, `observed*`
    b. Use the data frame produced by study designs to produce arrays of observed estimates and corresponding standard errors (with dummy value where missing), `est*` and `est*_sd`
    c. Assume that deviation from true parameter of interest (`error`) is driven by use of estimator
3. We then declare the relevant estimands and run diagnosis

```{r stan_meta, eval=FALSE}

stan_model_meta <- " 
  data {
    int<lower=0> N;   // number of studies 
    int<lower=0> K;   // max number of estimator (estimator-sampling pairs) 
    // number of studies with estimator (estimator-sampling pair)
    int<lower=0,upper=N> N1;
    int<lower=0,upper=N> N2;
    int<lower=0,upper=N> N3;
    // ids of studies with specific estimator (estimator-sampling pair)
    int<lower=0,upper=N> observed1[N1];   
    int<lower=0,upper=N> observed2[N2];
    int<lower=0,upper=N> observed3[N3];
    // parameter estimates
    real<lower=0,upper=1> est1[N1];   
    real<lower=0,upper=1> est2[N2];
    real<lower=0,upper=1> est3[N3];
    // estimated standard errors of parameter estimates
    real<lower=0> est1_sd[N1]; 
    real<lower=0> est2_sd[N2];
    real<lower=0> est3_sd[N3];
  }
  parameters {
    // (additive) error factor for each estimator/estimator-sampling pair
    real<lower=-1,upper=1> error[K]; 
    // prevalence estimate for each study
    vector<lower=0,upper=1>[N] alpha;
    // need to add Sigma to allow for interdependence of errors across estimators
    // or studies
  }

  model
    target += normal_lpmf(est1 | error[1] + alpha[observed1], est1_sd);
    target += normal_lpmf(est2 | error[2] + alpha[observed2], est2_sd);
    target += normal_lpmf(est3 | error[3] + alpha[observed3], est3_sd);
  }
  "

get_meta_estimands <- function(data) {
  
  data.frame(estimand_label = c(paste0("prevalence_", 1:N)),
             estimand = c(data[,1]),
             stringsAsFactors = FALSE)
}

get_meta_estimators = function(data) {
  
  stan_data <- list(N = nrow(data),
                    K = (ncol(data)-1)/2)
  
  for (k in 1:stan_data$K) {
    stan_data[[ paste0("observed",k) ]] <- 
      which(!is.na(data[,(2 * k)]))
    stan_data[[ paste0("N",k) ]] <- 
      length(stan_data[[paste0("observed",k)]])
    stan_data[[ paste0("est",k) ]] <- 
      data[stan_data[[paste0("observed",k)]],(2 * k)]
    stan_data[[ paste0("est",k,"_sd") ]] <- 
      data[stan_data[[paste0("observed",k)]],(1 + 2 * k)]
  }
  
  fit <- 
    rstan::stan(fit = stan_model_meta, 
                data = stan_data, 
                iter = 4000) %>% 
    extract
  
  data.frame(estimator_label = c(paste0("prev_", 1:N)),
             estimate = c(apply(fit$alpha, 2, mean)),
             sd =   c(apply(fit$alpha, 2, sd)),
             estimand_label = c(paste0("hidden_prev", 1:N)),
             big_Rhat = big_Rhat
             )
  
  }

```

## Meta declaration

### Additional study

```{r example_study_2}

study_2 <- 
  list(
    pop = 
      list(
        handler = get_study_population,
        network_handler = sim_block_network,
        network_handler_args = 
          list(N = 5000, K = 3, 
               prev_K = c(known_1 = .3, known_2 = .2, known_3 = .1), 
               rho_K = c(.1, .1, .1),
               p_edge_within = list(known_1 = c(0.2, 0.2), 
                                    known_2 = c(0.2, 0.2), 
                                    hidden = c(0.1, 0.9)),
               p_edge_between = list(known_1 = 0.1, 
                                     known_2 = 0.1, 
                                     hidden = 0.01),
               directed = FALSE),
        
        group_names = c("known_1", "known_2", "hidden"),
        
        # probability of visibility (show-up) for each group
        p_visibility = list(known_1 = .99, known_2 = .99, hidden = .6),
        
        # probability of service utilization in hidden population
        # for service multiplier
        add_groups = list(p_service = 0.3, 
                          loc_1 = 0.3, loc_2 = 0.1, loc_3 = 0.2)
      ),
    sample = 
      list(
        rds = list(handler = sample_rds,
                   # RDS parameters
                   sampling_variable = "rds",
                   n_seed = 100,
                   n_coupons = 3,
                   target_type = "waves",
                   target_n_rds = 2),
        pps = list(handler = sample_pps,
                   sampling_variable = "pps",
                   # prop sampling parameters
                   target_n_pps = 1000)
      ),
    estimands = list(handler = get_study_estimands),
    estimators = 
      list(
        rds = 
          list(
            chords = list(handler = get_study_est_chords, 
                          type = "integrated",
                          label = "rds_chords")
          ),
        pps = 
          list(
            ht = list(handler = get_study_est_ht, label = "pps_ht"),
            nsum = list(handler = get_study_est_nsum, label = "pps_nsum")
          )
      )
  )

```

### Declare multiple studies

```{r meta_study}

pops_args <- 
  list(study_1 = study_1$pop,
       study_2 = study_2$pop)

samples_args <- 
  list(study_1 = study_1$sample,
       study_2 = study_2$sample)

estimators_args <- 
  list(study_1 = study_1$estimators,
       study_2 = study_2$estimators)

estimands_args <- 
  list(study_1 = study_1$estimands,
       study_2 = study_2$estimands)


multi_population <- 
  declare_population(handler = get_multi_populations, 
                     pops_args = pops_args)

set.seed(19872312)
multi_population()

multi_sampling <- 
  declare_sampling(handler = get_multi_samples, 
                   samples_args = samples_args) 

set.seed(19872312)
draw_data(multi_population + multi_sampling)

multi_estimands <- 
  declare_estimand(handler = get_multi_estimands, 
                   estimands_args = estimands_args) 

multi_estimators <-
  declare_estimator(handler = get_multi_estimates,
                    estimators_args = estimators_args)

set.seed(19872312)
draw_estimands(multi_population + multi_sampling + multi_estimands + multi_estimators)
draw_estimates(multi_population + multi_sampling + multi_estimands + multi_estimators)

```
