---
title: "Methodological details"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Methodological details}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: hidden_population.bib
biblio-style: "apalike"
link-citations: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE,
  echo = TRUE,
  fig.path = "vignette-",
  message = FALSE,
  warning = FALSE
)

```

## Individual studies {#sec-estimation-study}

For each of the studies we are aiming to analyze all possible sampling-estimation method pairs given the sampling strategies used. Table below shows all sampling-estimation method pairs we consider in the meta-analysis. Note that the first three sampling-estimation pairs aim directly to estimate prevalence of hidden group within broader population, while the rest of the methods estimate size of the hidden group that can be transformed into prevalence estimate under assumption that there is no uncertainty about the size of the population within which the prevalence is being estimated.

| Sampling                       | Estimation                                                                                                                                                  | Method references                             | [R] Package                                                                                       |
|--------------------------------|-------------------------------------------------------------------------------------------------------------------------------------------------------------|-----------------------------------------------|---------------------------------------------------------------------------------------------------|
| **Prevalence estimation**      |                                                                                                                                                             |                                               |                                                                                                   |
| **PPS**                        | **HT**: Horvitz-Thompson estimator of [*prevalence*]{.underline} with re-scaled bootstrap standard errors                                                   | @rust1996variance                             | Self-coded + `surveybootstrap` [@feehan2023surveybootstrap]                                       |
| **TLS**                        | **HT**: Horvitz-Thompson estimator of [*prevalence*]{.underline} with re-scaled bootstrap standard errors [@rust1996variance]                               | @rust1996variance                             | Self-coded + `surveybootstrap` [@feehan2023surveybootstrap]                                       |
| **RDS**                        | **SS**: Sequential sampling estimator of [*prevalence*]{.underline}                                                                                         | @gile2011improved                             | `RDS` [@handcock2023rds]                                                                          |
| **Population size estimation** |                                                                                                                                                             |                                               |                                                                                                   |
| **PPS**                        | **NSUM**: Network scale-up estimatior of [*population size*]{.underline} with re-scaled bootstrap standard errors                                           | @killworth1998social; @rust1996variance       | `networkreporting` [@feehan2021networkreporting] + `surveybootstrap` [@feehan2023surveybootstrap] |
| **TLS**                        | **NSUM**: Network scale-up estimatior of [*population size*]{.underline} with re-scaled bootstrap standard errors [@killworth1998social; @rust1996variance] | @killworth1998social; @rust1996variance       | `networkreporting` [@feehan2021networkreporting] + `surveybootstrap` [@feehan2023surveybootstrap] |
| **TLS**                        | **RECAP \***: Mark-recapture estimator of [*population size*]{.underline} with parametric standard errors                                                   | @hickman2006estimating                        | `Rcapture` [@baillargeon2007rcapture]                                                             |
| **RDS**                        | **SSPSE**: Bayesian sequential sampling model of [*population size*]{.underline}                                                                            | @handcock2014                                 | `sspse` [@handcock2022sspse]                                                                      |
| **RDS**                        | **CHORDS**: Epidemiological model for [*population size*]{.underline} estimation                                                                            | @berchenko2017                                | `chords` [@berchenko2017]                                                                         |
| **RDS**                        | **MULTIPLIER** \*: Service-multiplier [*population size*]{.underline} estimator with bootstrap re-sampling standard errors                                  | @hickman2006estimating; @salganik2006variance | Self-coded + `surveybootstrap` [@feehan2023surveybootstrap]                                       |
| **RDS \***                     | **LINK**: Link-tracing [*population size*]{.underline} estimator based on special type of RDS                                                               | @vincent2019                                  | Self-coded based on @vincent2019                                                                  |

: Sampling-estimation pairs

In the meta-analysis part we focus on comparison of prevalence estimates produced by all the methods listed in the table. The sampling and estimation methods marked with `*` in the table indicate need for additional data or special type of sampling required for corresponding method. Specifically, estimation using *TLS-RECAP* requires recapture data to be collected beyond standard NSUM and direct indicators. *RDS-MULTIPLIER* estimation requires data from a provider of a service that is likely to be used by hidden group of interest as well as direct questions about that service use asked from hidden group members in RDS sample. Finally *RDS-LINK* estimation requires a special type of RDS sample with more initial seeds but less waves of link tracing and collection of data on recaptures in RDS network.

## Meta level {#sec-estimation-meta}

We use a Bayesian model to assess the relative bias of methods. We describe a model for $N$ sites and $K$ estimation methods which could be used at each site.

We are interested in the true prevalence, an $N$-dimensional vector $\alpha$ and the bias associated with each estimate relative to the benchmark procedure: a $K$-dimensional vector $\beta$ (with the first element constrained to unity).

The following code block describes the `stan` model used to estimate $\alpha$ and $\beta$ give the findings across studies.

```{r}
#| label: stancode
#| eval: true
#| echo: true

model_code <- "

data {
  int<lower=0> N;
  int<lower=0> K;
  int<lower=0> n_ests;
  real<lower=0> alpha_prior_mean[N];
  real<lower=0> alpha_prior_sd[N];
  real<lower=0> bias_prior_mean[K];
  real<lower=0> bias_prior_sd[K];
  int<lower=0> site[n_ests];
  int<lower=0> design[n_ests];
  vector<lower=0>[n_ests] ests;
  vector<lower=0>[n_ests] ses;
}
parameters {
  vector<lower=0.01>[K] bias;
  vector<lower=1>[N] alpha;
}

model {

  target += normal_lpdf(ests | bias[design].*alpha[site], ses);
  alpha ~ normal(alpha_prior_mean, alpha_prior_sd);
  bias ~ lognormal(log(bias_prior_mean), bias_prior_sd);

}
"


```

The model block has three main elements:

-   We assume that the likelihood of a given estimate $\hat{\alpha}_{ij}$ for estimand $\alpha_i$ using method $j$ in location $i$ is $\phi(\hat{\alpha}_{ij}|\beta_j\alpha_{i}, \hat{\sigma_{ij}})$.
-   We have a (wide) prior on $\alpha$: $\alpha_i \sim f(\mu_{\alpha, i}, {\sigma}_{\alpha, i})$, where the $\mu_{\alpha, i}$ is gathered from teams, $\sigma\_{\alpha}$ is large, and $f$ denotes the normal distribution. Note that we assume no relation between different elements of $\alpha$---that is we do not make use of a prior distribution on prevalence "in general."
-   We have a (wide) prior on $\beta_j$: $\beta_j \sim g(\mu_{\beta_j}, {\sigma}_{\beta_j})$, where the $\mu_{\beta_j}$ is gathered from teams, $\sigma_{\alpha}$ is large, and $g$ denotes the log-normal distribution. Note that we assume no relation between different elements of $\beta$---that is we do not make use of a prior distribution about biases of different methods "in general."

The model thus builds in a critical assumption that the relative bias of a method is constant across sites. It is this bias that is estimated. To be clear the assumption is not that one method will always produce a higher or lower estimate than another but simply that it is potentially biased in that *in expectation* it produces a higher or lower estimate than another. Bias is relative to the bias of the benchmark method and also to the truth to the extent that the benchmark method is itself unbiased.
