---
title: "hiddenmeta workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hiddenmeta workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE,
  echo = TRUE,
  fig.path = "vignette-",
  message = FALSE,
  warning = FALSE
)

```

## Install and load packages

```{r install, eval=FALSE}

install.packages("DeclareDesign")
install.packages("igraph")

devtools::install_github("gerasy1987/hiddenmeta", build_vignettes = TRUE)

```

```{r setup}

library(hiddenmeta)
library(DeclareDesign)
library(igraph)
library(knitr)

```

## Step 1. Provide study design features

```{r example_study_1}

## STUDY 1
study_1 <- 
  list(
    pop = 
      list(
        handler = get_study_population,
        
        # network structure setup
        network_handler = sim_block_network,
        network_handler_args = 
          list(N = 2000, K = 2, prev_K = c(known = .3, hidden = .1), rho_K = .3,
               p_edge_within = list(known = c(0.05, 0.1), hidden = c(0.05, 0.7)),
               p_edge_between = list(known = 0.05, hidden = 0.05),
               directed = FALSE),
        
        # groups
        group_names = c("known", "hidden"),
        
        # probability of visibility (show-up) for each group
        p_visible = list(known = 1, hidden = .7),
        
        # probability of service utilization in hidden population
        # for service multiplier
        add_groups = 
          list(service_use = "rbinom(n(), 1, 0.25 + hidden * 0.05)",
         "purrr::map_df(hidden, ~ sapply( `names<-`(c(.2, .1, .3, .2), paste0('loc_', 1:4)), function(add) rbinom(length(.x), 1, 0.1 + .x * add)))",
         known_2 = 0.1, known_3 = 0.2)
      ),
    sample = 
      list(
        rds = list(handler = sample_rds,
                   # RDS parameters
                   sampling_variable = "rds",
                   hidden_var = "hidden", # default
                   n_seed = 20,
                   n_coupons = 3,
                   target_type = "sample",
                   target_n_rds = 100),
        tls = list(handler = sample_tls,
                   sampling_variable = "tls",
                   # TLS sampling parameters
                   target_n_clusters = 3,
                   target_n_tls = 300,
                   cluster = paste0("loc_", 1:4)),
        pps = list(handler = sample_pps,
                   sampling_variable = "pps",
                   # prop sampling parameters
                   sampling_frame = NULL,
                   strata = NULL,
                   cluster = NULL,
                   target_n_pps = 400)
      ),
    inquiries = list(handler = get_study_estimands,
                     known_pattern = "^known$", 
                     hidden_var = "hidden"),
    estimators = 
      list(
        rds = 
          list(sspse = list(handler = get_study_est_sspse,
                            prior_mean = 200,
                            mcmc_params = list(interval = 5, burnin = 2000, samplesize = 500),
                            total = 2000,
                            rds_prefix = "rds", 
                            label = "rds_sspse"),
               chords = list(handler = get_study_est_chords, 
                             type = "mle",
                             seed_condition = "rds_from == -999",
                             n_boot = 100,
                             rds_prefix = "rds",
                             label = "rds_chords"),
               multiplier = list(handler = get_study_est_multiplier, 
                                 service_var = "service_use",
                                 seed_condition = "rds_from == -999",
                                 n_boot = 100,
                                 rds_prefix = "rds",
                                 label = "rds_multi")),
        tls =
          list(ht = list(handler = get_study_est_ht,
                         weight_var = "tls_weight",
                         prefix = "tls",
                         label = "tls_ht"),
               nsum = list(handler = get_study_est_nsum,
                           known = c("known", "known_2", "known_3"),
                           hidden = "hidden_visible_out",
                           survey_design = ~ tls_cluster,
                           n_boot = 100,
                           prefix = "tls",
                           label = "tls_nsum"),
               recap = list(handler = get_study_est_recapture,
                            capture_vars = paste0("loc_", 1:4),
                            sample_condition = "tls == 1",
                            model = "Mt",
                            hidden_condition = "hidden == 1",
                            label = "tls_recap")),
        pps = 
          list(ht = list(handler = get_study_est_ht,
                         prefix = "pps",
                         label = "pps_ht"),
               nsum = list(handler = get_study_est_nsum,
                           known = c("known", "known_2", "known_3"),
                           hidden = "hidden_visible_out",
                           survey_design = ~ pps_cluster + strata(pps_strata),
                           n_boot = 100,
                           prefix = "pps",
                           label = "pps_nsum")),
        all = 
          list(recap1 = list(handler = get_study_est_recapture,
                             capture_vars = c("rds", "pps"),
                             model = "Mt",
                             hidden_condition = "hidden == 1",
                             label = "rds_pps_recap"),
               recap2 = list(handler = get_study_est_recapture,
                             capture_vars = c("rds", paste0("loc_", 1:4)),
                             model = "Mt",
                             hidden_condition = "hidden == 1",
                             label = "rds_tls_recap"))
      )
  )

```

## Step 2. Declare study population

```{r example_pop}

study_population <-
  eval(as.call(c(list(declare_population), study_1$pop)))

set.seed(19872312)
example_pop <- study_population()

example_pop %>% 
  dplyr::sample_n(n()) %>% # shuffle data frame
  rmarkdown::paged_table(options = list(rows.print = 15))

```

### Show the network

```{r plot_pop_network, fig.width=6, fig.height=8}

g <-
  example_pop %$% {
    hiddenmeta:::retrieve_graph(links) %>%
      igraph::set_vertex_attr("name", value = name) %>%
      igraph::set_vertex_attr("type", value = type)
  }

igraph::V(g)$color <-
  plyr::mapvalues(igraph::V(g)$type,
                  from = unique(igraph::V(g)$type),
                  to = grDevices::palette.colors(n = length(unique(igraph::V(g)$type)), 
                                                 palette = "Set 3"))

plot(g,
     layout = igraph::layout_on_grid(g, dim = 2, width = 100),
     vertex.size = 3, vertex.dist = 2, vertex.label = NA, edge.width = 1,
     edge.arrow.size = .2, edge.curved = .2)

legend(x = -1, y = -1.2,
       legend = c("none", "known only", "hidden only", "both"),
       pt.bg = grDevices::palette.colors(n = length(unique(igraph::V(g)$type)), palette = "Set 3"),
       pch = 21, col = "#777777", pt.cex = 2, cex = 1.5, bty = "o", ncol = 2)

```

## Step 3. Declare all relevant study sampling procedures

The sampling procedures are additive in a sense that each procedure appends several columns relevant to the sampling procedure and particular draw based on population simulation, but does not change the study population data frame (unless you specify `drop_nonsampled = TRUE`).

```{r example_rds}

study_sample_rds <- 
  eval(as.call(c(list(declare_sampling), study_1$sample$rds)))

set.seed(19872312)
draw_data(study_population + study_sample_rds) %>%  
  dplyr::sample_n(n()) %>% # shuffle data frame
  rmarkdown::paged_table(options = list(rows.print = 15))

```

```{r example_pps}

study_sample_pps <- 
  eval(as.call(c(list(declare_sampling), study_1$sample$pps)))

set.seed(19872312)
draw_data(study_population + study_sample_rds + study_sample_pps) %>% 
  dplyr::sample_n(n()) %>% # shuffle data frame
  rmarkdown::paged_table(options = list(rows.print = 15))

```

```{r example_tls}

study_sample_tls <- 
  eval(as.call(c(list(declare_sampling), study_1$sample$tls)))

set.seed(19872312)
draw_data(study_population + 
            study_sample_rds + study_sample_pps + study_sample_tls) %>% 
  dplyr::sample_n(n()) %>% # shuffle data frame
  rmarkdown::paged_table(options = list(rows.print = 15))

```

## Step 4. Declare study level estimands

```{r example_estimands}

study_estimands <- 
  eval(as.call(c(list(declare_inquiry), study_1$inquiries)))

set.seed(19872312)
draw_inquiry(study_population + 
                # study_sample_rds + study_sample_pps + study_sample_tls + 
                study_estimands) %>% 
  kable(digits = 2)

```

## Step 5. Declare estimators used in the study

```{r example_estimators}

est_sspse <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$rds$sspse)))
est_chords <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$rds$chords)))
est_multi <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$rds$multiplier)))

est_ht_pps <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$pps$ht)))
est_nsum_pps <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$pps$nsum)))

est_ht_tls <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$tls$ht)))
est_nsum_tls <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$tls$nsum)))
est_recap_tls <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$tls$recap)))

est_recap_rds_pps <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$all$recap1)))
est_recap_rds_tls <- 
  eval(as.call(c(list(declare_estimator), study_1$estimators$all$recap2)))

set.seed(19872312)
draw_estimates(study_population +
                 study_sample_rds + study_sample_pps + study_sample_tls +
                 study_estimands +
                 est_sspse + est_chords + est_multi +
                 est_nsum_pps + est_ht_pps +
                 est_nsum_tls + est_ht_tls + est_recap_tls +
                 est_recap_rds_pps + est_recap_rds_tls) %>%
  kable(digits = 2)

```

## Step 6. Declare full study

```{r example_study, warning=FALSE}

study1 <- 
  study_population +
  study_sample_rds + study_sample_pps + study_sample_tls +
  study_estimands +
  est_sspse + est_chords + est_multi +
  est_nsum_pps + est_ht_pps +
  est_nsum_tls + est_ht_tls + est_recap_tls +
  est_recap_rds_pps + est_recap_rds_tls

# can draw one of the samples
study1$study_sample_rds(study1$study_population())

# can draw full data
study1_data <- draw_data(study1)

# can draw estimands
study1$inquiry(study1_data)

# can draw any of the estimators
study1$rds_sspse(study1_data)
study1$pps_ht(study1_data)
study1$rds_pps_recap(study1_data)

```


## Step 7. Diagnose study design

```{r example_diagnose, warning = FALSE, eval=FALSE}

study_diagnosands <-
 declare_diagnosands(
    mean_estimand = mean(estimand),
    mean_estimate = mean(estimate),
    sd_estimate = sd(estimate),
    mean_se = mean(se),
    bias = mean(estimate - estimand),
    rmse = sqrt(mean((estimate - estimand) ^ 2))
  )

study1_simulations <- simulate_design(study1, sims = 10)

diagnose_design(study1_simulations, 
                diagnosands = study_diagnosands, sims = 2) %>% 
  reshape_diagnosis %>% select(-'Design Label') %>%
  kable()

```

## Multi study declaration

### Additional study

```{r example_study_2}

study_2 <- 
  list(
    pop = 
      list(
        handler = get_study_population,
        network_handler = sim_block_network,
        network_handler_args = 
          list(N = 5000, K = 3, 
               prev_K = c(frame = .5, known = .2, hidden = .1), 
               rho_K = c(.05, .05, .05),
               p_edge_within = list(frame = c(0.05, 0.05), 
                                    known = c(0.1, 0.05), 
                                    hidden = c(0.2, 0.9)),
               p_edge_between = list(frame = 0.05, 
                                     known = 0.1, 
                                     hidden = 0.01),
               directed = FALSE),
        
        group_names = c("frame", "known", "hidden"),
        
        # probability of visibility (show-up) for each group
        p_visible = list(frame = 1, known = 1, hidden = .6),
        
        # probability of service utilization in hidden population
        # for service multiplier
        
        add_groups = 
          list(service_use = "rbinom(n(), 1, 0.25 + hidden * 0.3)",
               "purrr::map_df(hidden, ~ sapply( `names<-`(runif(10, 0.05,.3), paste0('loc_', 1:10)), function(add) rbinom(length(.x), 1, 0.1 + .x * add)))",
               known_2 = 0.1, known_3 = 0.2)
      ),
    sample = 
      list(
        rds = list(handler = sample_rds,
                   # RDS parameters
                   sampling_variable = "rds",
                   hidden_var = "hidden",
                   n_seed = 100,
                   n_coupons = 3,
                   target_type = "waves",
                   target_n_rds = 2),
        tls = list(handler = sample_tls,
                   sampling_variable = "tls",
                   # TLS sampling parameters
                   target_n_clusters = 4,
                   target_n_tls = 300,
                   cluster = paste0("loc_", 1:8)),
        pps = list(handler = sample_pps,
                   sampling_variable = "pps",
                   # prop sampling parameters
                   sampling_frame = "frame",
                   strata = NULL,
                   cluster = NULL,
                   target_n_pps = 800)
      ),
    inquiries = list(handler = get_study_estimands,
                     known_pattern = "^known$|^frame$", 
                     hidden_var = "hidden"),
    estimators = 
      list(
        rds = 
          list(sspse = list(handler = get_study_est_sspse, 
                            label = "rds_sspse",
                            prior_mean = 450,
                            mcmc_params = list(interval = 5, burnin = 2000, samplesize = 500),
                            total = 5000,
                            rds_prefix = "rds"),
               chords = list(handler = get_study_est_chords, 
                             type = "mle",
                             label = "rds_chords",
                             seed_condition = "rds_from == -999",
                             n_boot = 100,
                             rds_prefix = "rds"),
               multiplier = list(handler = get_study_est_multiplier, 
                                 service_var = "service_use",
                                 seed_condition = "rds_from == -999",
                                 n_boot = 100,
                                 rds_prefix = "rds",
                                 label = "rds_multi")),
        tls =
          list(ht = list(handler = get_study_est_ht,
                         weight_var = "tls_weight",
                         prefix = "tls",
                         label = "tls_ht"),
               nsum = list(handler = get_study_est_nsum,
                           known = c("known", "frame"),
                           hidden = "hidden_visible_out",
                           survey_design = ~ tls_cluster,
                           n_boot = 100,
                           prefix = "tls",
                           label = "tls_nsum"),
               recap = list(handler = get_study_est_recapture,
                            capture_vars = paste0("loc_", 1:8),
                            sample_condition = "tls == 1",
                            model = "Mt",
                            hidden_condition = "hidden == 1",
                            label = "tls_recap")),
        pps = 
          list(
            ht = list(handler = get_study_est_ht, 
                      label = "pps_ht"),
            nsum = list(handler = get_study_est_nsum,
                        known = c("frame", "known"),
                        hidden = "hidden_visible_out",
                        survey_design = ~ pps_cluster + strata(pps_strata),
                        n_boot = 100,
                        label = "pps_nsum")),
        all = 
          list(recap1 = list(handler = get_study_est_recapture,
                             capture_vars = c("rds", "pps"),
                             model = "Mt",
                             hidden_condition = "hidden == 1",
                             label = "rds_pps_recap"),
               recap2 = list(handler = get_study_est_recapture,
                             capture_vars = c("rds", paste0("loc_", 1:8)),
                             model = "Mt",
                             hidden_condition = "hidden == 1",
                             label = "rds_tls_recap"))
      )
  )

```

### Declare multiple studies

```{r multi_study, eval=TRUE, warning=FALSE}

multi_population <- 
  declare_population(handler = get_multi_populations, 
                     pops_args = list(study_1 = study_1$pop,
                                      study_2 = study_2$pop))

multi_sampling <- 
  declare_sampling(handler = get_multi_samples, 
                   samples_args = list(study_1 = study_1$sample,
                                       study_2 = study_2$sample)) 

multi_inquiry <- 
  declare_inquiry(handler = get_multi_estimands, 
                  inquiries_args = list(study_1 = study_1$inquiries,
                                        study_2 = study_2$inquiries)) 

multi_estimators <-
  declare_estimator(handler = get_multi_estimates,
                    estimators_args = list(study_1 = study_1$estimators,
                                           study_2 = study_2$estimators))

multi_study <- multi_population + multi_sampling + multi_inquiry + multi_estimators

set.seed(19872312)
draw_inquiry(multi_study) %>% 
  kable()

draw_estimates(multi_study) %>% 
  kable()

```

### Diagnose multiple studies

```{r multi_study_diagnose, eval=FALSE}

multi_simulations <- simulate_design(multi_study, sims = 10)

diagnose_design(simulations_df = multi_simulations, 
                diagnosands = study_diagnosands) %>% 
  reshape_diagnosis %>% select(-'Design Label') %>%
  kable()

```


## Meta-analysis structure

1. Conduct multi-study design for as many sampling-estimator pairs in each study as possible, then diagnoise the multi-study design. Calculate average (across simulations) estimand and bias of sampling-estimator for each of the studies and estimator sampling strategies. These will serve as population we will be drawing population-sampling-estimator triads

2. Estimands include:
    - Average estimand by inquiry label (within study)
    - Average bias of specific sampling-estimator pair (across studies) compared to truth
    - Average relative bias of sampling-estimator pair (across studies) compared to "gold standard"
    - Ratio of average bias to costs of sampling-estimator pair 

3. As mentioned before sampling will consist of drawing population-sampling-estimator triads from the population presuming that each study uses at least two sampling strategies at a time

4. Once we draw sample we use Stan model to estimate study-specific estimands and sampling-estimator specific errors (biases)

5. We have all parts to conduct the full cycle of meta-analyses


```{r meta_study, eval=FALSE}

meta_population <- 
  declare_population(multi_design = multi_study, n_sim = 10, parallel = TRUE, 
                     handler = get_meta_population)

meta_inquiry <- 
  declare_inquiry(study_estimand = "hidden_size",
                  samp_est_benchmark = "pps_ht", 
                  handler = get_meta_estimands)

meta_sample <- 
  declare_population(sampling_variable = "meta",
                     selection_variables = c("sample", "estimator"),
                     samples_per_study = 2, estimator_per_sample = 3, 
                     handler = get_meta_sample)

set.seed(19872312)
meta_pop <- meta_population()
draw_inquiry(meta_population + meta_inquiry)
draw_data(meta_population + meta_inquiry + meta_sample)



```


```{r meta_study_diagnose, eval=FALSE}

# meta_population <- 
#   declare_estimand(handler = get_meta_population)
#   
# meta_estimands <- 
#   declare_estimand(handler = get_meta_estimands)
# 
# meta_estimators <- 
#   declare_estimator(handler = get_meta_estimators)
# 

meta_design <- meta_population + meta_inquiry + meta_estimators
 
```
